---
title: "R Notebook"
output: git documents
---

```{bash}
sudo apt-get update -y
sudo apt-get install -y libglpk-dev 
sudo apt-get install -y liblzma-dev libbz2-dev
```

```{r}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("BiocStyle")
BiocManager::install("Rhtslib")
```

```{r}
library("knitr")
library("BiocStyle")
.cran_packages <-c ("ggplot2", "gridExtra", "devtools")
install.packages(.cran_packages) 
.bioc_packages <- c("dada2", "phyloseq", "DECIPHER", "phangorn")
BiocManager::install(.bioc_packages)# Load packages into session, and print package version
sapply(c(.cran_packages, .bioc_packages), require, character.only = TRUE)
```

```{r}
sapply(c(.cran_packages, .bioc_packages), require, character.only = TRUE)
```

```{r}
install.packages("gitcreds")
library(gitcreds)
gitcreds_set()
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
